Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-06-19 WSSSPE2_report/WSSSPE2_review.tex
Typeset space as normal inter-word space

Two main avenues could be used to implement policy that would improve reproducibility and drive top-down culture change:
\begin{itemize}
\item Funders can aim to get more software expertise on to funding review panels and provide more guidance on what is required of software related to research (cf. data management plans)
\item Journals can define and publish journal policies to improve reproducibility, and reviewers can insist that authors provide sufficient information and access to data and software to allow them reproduce the results in the paper. Stronger policies even for some high-impact journals have recently come into place, for example Nature Publishing journals.
\end{itemize}

>>>>

Two main avenues could be used to implement policy that would improve reproducibility and drive top-down culture change:
\begin{itemize}
\item Funders can aim to get more software expertise on to funding review panels and provide more guidance on what is required of software related to research (cf.\ data management plans)
\item Journals can define and publish journal policies to improve reproducibility, and reviewers can insist that authors provide sufficient information and access to data and software to allow them reproduce the results in the paper. Stronger policies even for some high-impact journals have recently come into place, for example Nature Publishing journals.
\end{itemize}
